---
title: "R Notebook"
output:
  pdf_document: default
  html_notebook: default
---

## Problem 2: Class Data

```{r, echo=FALSE, warning=FALSE, message=FALSE}
library(data.table)
library(pander)
Survey_Dat <- fread(input = "C:/Users/Echo/Desktop/2017 Fall/Statistical Package/HW8/Echo-Wei-HW/08_text_mining_Rnotebooks_bash_sed_awk/survey_data.txt", header = T, showProgress=F)
colnames(Survey_Dat) <- c("Major", "Platform", "Level", "Programming")

library(tidytext)
library(dplyr)
library(tidytext)

####### Major #########
library(ggplot2)
par(frow=c(1, 2))

c1 <- Survey_Dat[, 1]
c1_df <- data.frame(line = 1:14, text = c1)
c1_df %>%
  unnest_tokens(word, Major) %>%
  count(word, sort = TRUE) %>%
  filter(n > 2) %>%
  mutate(word = reorder(word, n)) %>%
  ggplot(aes(word, n)) +
  geom_col() +
  xlab(NULL) +
  coord_flip()

library(wordcloud)
c1_df %>%
  unnest_tokens(word, Major) %>%
  count(word) %>%
  with(wordcloud(word, n, max.words = 200))
```

From the plot, we can get that most students have bachelor degree with background at math.

```{r, echo=FALSE, warning=FALSE, message=FALSE}
######## Platform #######
c2 <- Survey_Dat[, 2]
c2_df <- data.frame(line = 1:14, text = c2)
c2_df %>%
  unnest_tokens(word, Platform) %>%
  count(word, sort = TRUE) %>%
  mutate(word = reorder(word, n)) %>%
  ggplot(aes(word, n)) +
  geom_col() +
  xlab(NULL) +
  coord_flip()

c2_df %>%
  unnest_tokens(word, Platform) %>%
  count(word) %>%
  with(wordcloud(word, n, max.words = 200))
```

From the plot, we can get most students use PC system.

```{r, echo=FALSE, warning=FALSE, message=FALSE}
##### R Level ##########
data(stop_words)
c3 <- Survey_Dat[, 3]
c3_df <- data.frame(line = 1:14, text = c3)
c3_df %>%
  unnest_tokens(word, Level) %>%
  anti_join(stop_words) %>%
  count(word, sort = TRUE) %>%
  mutate(word = reorder(word, n)) %>%
  ggplot(aes(word, n)) +
  geom_col() +
  xlab(NULL) +
  coord_flip()

c3_df %>%
  unnest_tokens(word, Level) %>%
  count(word) %>%
  with(wordcloud(word, n, max.words = 200))

```

From the graph, we can get most students think themselves as intermediate.

```{r, echo=FALSE, warning=FALSE, message=FALSE}
data(stop_words)
c4 <- Survey_Dat[, 4]
c4_df <- data.frame(line = 1:14, text = c4)
c4_df %>%
  unnest_tokens(word, Programming) %>%
  anti_join(stop_words) %>%
  count(word, sort = TRUE) %>%
  mutate(word = reorder(word, n)) %>%
  ggplot(aes(word, n)) +
  geom_col() +
  xlab(NULL) +
  coord_flip()

c4_df %>%
  unnest_tokens(word, Programming) %>%
  count(word) %>%
  with(wordcloud(word, n, max.words = 200))
```

From the graph, we can get 8 studetns have learnt SAS. Python and Matlab ranked second behind SAS.

## Problem 3

```{r, echo=FALSE, warning=FALSE, message=FALSE}
Car_dat <- fread(input = "C:/Users/Echo/Desktop/2017 Fall/Inference Fundamentals/Homework/HW4/Cohen_Data.csv", header = T, select=c(1,2), showProgress=F)
```

The data set is downloaded at http://lib.stat.cmu.edu/DASL/Datafiles/Cars.html.

The data set is about measurements on 38 1978-79 model automobiles. The gas mileage in miles per gallon as measured by Consumers' Union on a test track. Other values as reported by automobile manufacturer. The Cohen's d tests the difference of MPG(Miles per gallon, a measure of gas mileage) between cars produced by U.S. and that produced by other countries, including France, Germany, Italy, Japan and Sweden. 

```{r, echo=FALSE, warning=FALSE, message=FALSE}
Cou <- Car_dat[, 1]
Cou_df <- data.frame(line = 1:38, text = Cou)
Cou_df %>%
  unnest_tokens(word, Country) %>%
  anti_join(stop_words) %>%
  count(word, sort = TRUE) %>%
  mutate(word = reorder(word, n)) %>%
  ggplot(aes(word, n)) +
  geom_col() +
  xlab(NULL) +
  coord_flip()

Cou_df %>%
  unnest_tokens(word, Country) %>%
  count(word) %>%
  with(wordcloud(word, n, max.words = 200))
```

From the graph, we can get more than half of the cars been surveyed are manufactured by U.S..

```{r, echo=FALSE, warning=FALSE, message=FALSE}
Ca <- Car_dat[, 2]
Ca_df <- data.frame(line = 1:38, text = Ca)
Ca_df %>%
  unnest_tokens(word, Car) %>%
  anti_join(stop_words) %>%
  count(word, sort = TRUE) %>%
  filter(n >1) %>%
  mutate(word = reorder(word, n)) %>%
  ggplot(aes(word, n)) +
  geom_col() +
  xlab(NULL) +
  coord_flip()

Ca_df %>%
  unnest_tokens(word, Car) %>%
  count(word) %>%
  with(wordcloud(word, n, max.words = 200))
```

From the graph, we can get that wagon, ford and dodge are most popular.

## Problem 4

Account has been registered at arc.vt.edu..

\
\
```{r, ref.label=knitr::all_labels(),echo=TRUE,eval=FALSE}
```
